University of Florida Knowledge Base Acceleration Notebook

### 2013-10-18 paper/kbanotebook2013/content/implementation.tex
Updated yangs section for him to reviews

Our pipeline of processing the corpus consists of a two layer indexing system 
referred to as \textit{Chunk Files Index Generator} and \textit{StreamItems Index Generator}.
Chunk Files Index Generator will generate indexes of the chunk files 
that contain a mention of any of the desired entities. StreamItems Index Generator 
on the other hand will index StreamItems that contain a mention of a given entity 
respectively. This two level indexing will eliminate the need to process each and 
every ChunkFile/StreamItem for every entity. The reason for splitting this task 
into two steps is that not all chunk files contain any mention of the entities and 
we want to get rid of them as soon as possible. Chunk Files Index Generator which 
is written in C++ will discard non-mentioning chunk files and will stop further 
processing a chunk file as soon as it finds a mention there. Each chunk file can 
contain up to thousands of SIs which can be so time consuming if we were to 
process them in our Java base code.Processing StreamItems on the other hand is 
done in Java with ideas in mind for later on extensibility by adding other Java libraries.

@@

In the data set, we are given 4 months of data (October 2011 - February 2012) as training data.
Instead of building a classifier we use pattern matching methods to find
corresponding slot values for entities. 
Pattern matching is simple to manipulate results and implement.
Additionally, we can simply to explain and evaluate results.

@@

\begin{algorithm}
  \textbf{List of entities $\mathcal{E} = \{e_0, \ldots, e_{170}\}$}\\
  \textbf{List of Streamitems $\mathcal{S} = \{s_0, \ldots, s_{|\mathcal{S}|}\}$}\\
  \textbf{List of patterns $P = \{p_0, \ldots, p_{|P|}\}$}\\
  \begin{algorithmic}%[1]
    \FOR{$si \in \mathcal{S}$}
      \FOR{$sentence \in si$}
        %%\IF{check\_pattern(sentence, pattern)}
        \FOR{$pattern \in P$}
          \IF{Satisfies($sentence$, $pattern$)}
            \STATE Emit($sentence$, $pattern$)
          \ENDIF
        \ENDFOR
      \ENDFOR
    \ENDFOR
  \end{algorithmic}
\end{algorithm}

A pattern is defined as a record representing knowledge going to be added to a knowledge base.
A pattern $\mathcal{P}$ is represented as $\mathcal{P} = \langle p_1, p_2, p_3, p_4, p_5 \rangle$.

The first value, $p_1$ represents the type of entity. These entity types are in
the set $\{ \text{\tt FAC}, \text{\tt ORG}, \text{\tt PER} \}$ where \texttt{FAC}
represents a type of facility, \texttt{ORG} represents an organization and \texttt{PER}
represents a person.
The $p_2$ represents a slot name.
A list of slot names is present in Table~\ref{table:slotNameOntology}.
The third element $p_3$ is the pattern content. This is a string found in the sentence.
The extractor looks for this exact string or pattern in a sentence.
The pattern evaluator uses a direction (\texttt{left} or \texttt{right}) found in
$p_4$ to explore sentence.
The final element $p_5$ represent the slot value of a pattern. Thois
%When we match one pattern, we match all the 
%fields except the third field, which is extracted as the final result.
The type of slot value may be the entity 
type tagged by Lingpipe, a noun phrase (\texttt{NP}) tagged by OpenNLP or a hard-coded phrase. 
For these three kinds of patterns, we implement them in different 
ways accordingly. Next, we will explain the patterns with more details, an
example can be found in Figure~\ref{fig:pattern}.

\textbf{Slot value type, tagged by Lingpipe:} For slot FounderOf, we have this
pattern: $\langle$ \texttt{PER, FounderOf, ``founder'', right, ORG} $\rangle$. PER means 
that the entity we are finding slot values for is a PER entity; FounderOf 
means this is a pattern for FounderOf slot. Founder is the anchor word we are 
trying to match in the sentence text; right means that we are going to the 
right part of the sentence to match the pattern and find the slot value; ORG 
means the slot value should be a ORG entity.

\textbf{Slot value tagged as noun phrase by OpenNLP:} $\langle$ \texttt{PER, AwardsWon, ``awarded'', 
right, NP}$\rangle$, NP meaning noun phrase. This pattern can be interpreted 
as that we are looking for a noun phrase after the ``awarded'' since that noun 
phrase could possibly represent an award. Since titles and awards are usually 
not the Lingpipe entities, we use the OpenNLP noun phrase chunker to fetch the 
noun phrases.

\textbf{Slot value of time phrases, hard coded:} $\langle$ \texttt{PER, DateOfDeath, ``died'', right, 
``last night''}$\rangle$. In this pattern, ``last night'' means we are looking for 
exactly the phrase ``last night'' to the right of ``died''. This pattern is 
inspired by the intuition that in news articles, people often mention that 
somebody died last night instead of mentioning the accurate date information 
and Lingpipe tends not to tag phrases like ``last night'' as a DATE entity.

We have found that there are three major classes of accuracy errors:
wrong entities found, wrong tags by the Lingpipe, and finally wrong results matched 
by the patterns. We solve the first problem by using the Wikipedia or twitter 
information of the entities to get better alias names. And we use
post-processing to reduce the second and third types of errors (Section~\ref{section:highAccuracyFilter}).

@@

The SSF output of many extractions is noisy. The data contains duplicates and 
incorrect extractions. We can define rules to sanitize the output only using 
the information present in the SSF file. The file is processed in time order, 
in a tuple-at-a-time fashion to minimize the impact on accuracy. We define 
two classes of rules: deduplication rules and inference rules.

>>>>

Our pipeline of processing the corpus consists of a two layer indexing system 
referred to as \textit{Chunk Files Index Generator} and \textit{StreamItems Index Generator}.
Chunk Files Index Generator will generate indexes of the chunk files 
that contain a mention of any of the desired entities. StreamItems Index Generator 
on the other hand will index StreamItems that contain a mention of a given entity 
respectively. This two level indexing will eliminate the need to process each and 
every ChunkFile/StreamItem for every entity. The reason for splitting this task 
into two steps is that not all chunk files contain any mention of the entities and 
we want to get rid of them as soon as possible. Chunk Files Index Generator which 
is written in C++ discards non-mentioning chunk files and will stop further 
processing a chunk file as soon as it finds a mention there. Each chunk file can 
contain up to thousands of SIs which can be so time consuming if we were to 
process them in our Java base code.Processing StreamItems on the other hand is 
done in Java with ideas in mind for later on extensibility by adding other Java libraries.

@@

In the data set, we are given 4 months of data (October 2011 - February 2012) as training data.
Instead of building a classifier we use pattern matching methods to find
corresponding slot values for entities. 
Pattern matching is simple to manipulate results and implement.
Additionally, a classifier approach is more difficult to evaluate and explain results.

@@

\begin{algorithm}
  \caption{Streaming Slot Value Extraction Pseudocode}
  \textbf{List of entities $\mathcal{E} = \{e_0, \ldots, e_{170}\}$}\\
  \textbf{List of Streamitems $\mathcal{S} = \{s_0, \ldots, s_{|\mathcal{S}|}\}$}\\
  \textbf{List of patterns $P = \{p_0, \ldots, p_{|P|}\}$}\\
  \begin{algorithmic}%[1]
    \FOR{$si \in \mathcal{S}$}
      \FOR{$sentence \in si$}
        %%\IF{check\_pattern(sentence, pattern)}
        \FOR{$pattern \in P$}
          \IF{Satisfies($sentence$, $pattern$)}
            \STATE Emit($sentence$, $pattern$) // Deal specifically with the three types
          \ENDIF
        \ENDFOR
      \ENDFOR
    \ENDFOR
  \end{algorithmic}
\end{algorithm}

\subsubsection{Types of patterns}
A pattern is defined as a record representing knowledge going to be added to a knowledge base.
A pattern $\mathcal{P}$ is represented as a five-tuple $\mathcal{P} = \langle p_1, p_2, p_3, p_4, p_5 \rangle$.

The first value, $p_1$ represents the type of entity. These entity types are in
the set $\{ \text{\tt FAC}, \text{\tt ORG}, \text{\tt PER} \}$ where \texttt{FAC}
represents a type of facility, \texttt{ORG} represents an organization and \texttt{PER}
represents a person.
The $p_2$ represents a slot name.
A list of slot names is present in Table~\ref{table:slotNameOntology}.
The third element $p_3$ is the pattern content. This is a string found in the sentence.
The extractor looks for this exact string or pattern in a sentence.
The pattern evaluator uses a direction (\texttt{left} or \texttt{right}) found in
$p_4$ to explore sentence.
The final element $p_5$ represent the slot value of a pattern. Thois
%When we match one pattern, we match all the 
%fields except the third field, which is extracted as the final result.
The type of slot value may be the entity 
type tagged by Lingpipe, a noun phrase (\texttt{NP}) tagged by OpenNLP or a hard-coded phrase. 
For these three kinds of patterns, we implement them in different 
ways accordingly. Next, we explain the patterns with more details, an
example can be found in Figure~\ref{fig:pattern}.

\textbf{Type I.} This pattern type is driven by the slot value type, a pattern
tagged by Lingpipe. For example, pattern
$\langle$\texttt{PER, FounderOf, \textit{founder}, right, ORG}$\rangle$. \texttt{PER} means 
that the entity we are finding slot values for a PER entity; \texttt{FounderOf} 
means this is a pattern for FounderOf slot. \textit{founder} is the anchor word we are 
match in a sentence; \texttt{right} means that we are going to the 
right part of the sentence to match the pattern and find the slot value; ORG 
means the slot value should be a ORG entity.

\textbf{Type II.} This pattern type is unique because it only looks for a
slot value tagged as noun phrase (NP) by OpenNLP.\@ For example,
pattern $\langle$\texttt{PER, AwardsWon, \textit{awarded}, 
right, NP}$\rangle$. This pattern can be interpreted 
as that we are looking for a noun phrase after the \textit{awarded} since that noun 
phrase may represent an award. Titles and awards are usually 
not the Lingpipe entities, hence the use of the OpenNLP noun phrase chunker to fetch the 
noun phrases.

\textbf{Type III.} Some relations are best discovered by hard coding the slot values.
Examples of these include time phrases: $\langle$\texttt{PER, DateOfDeath, \textit{died}, right, 
\textit{last night}}$\rangle$. In this pattern, \textit{last night} means we are looking for 
exactly the phrase \textit{last night} to the right of \textit{died}. This pattern is 
inspired by the intuition that in news articles, people often mention that 
somebody died last night instead of mentioning the accurate date information 
and Lingpipe tends not to tag phrases like \textit{last night} as a DATE entity.

We sampled documents from the training data period to generate an initial set of
patterns. We then use these patterns to generate SSF results. By manully looking at these results, we
prune some patterns with poor­performance and add more patterns that we identified from these results.
We use several iterations to find the best patterns.
We found that it is time consuming to identity quality pattern.

We found three major classes of accuracy errors:
incorrect entities selected, incorrect tags by Lingpipe and incorrect pattern extractions.
The first issue is ameliorated by generating better aliases (Section~\ref{section:aliasgeneration}). And we use
post-processing to reduce the second and third types of errors (Section~\ref{section:highAccuracyFilter}).
We didn't use more advanced NLP packages such as Stanford NLP because of the large size of the data set.
The post-processing step to improve the results is discussed in the next section.

@@

The SSF output of streaming slot value extraction is noisy. The data contains duplicates and 
incorrect extractions. We can define rules to sanitize the output only using 
the information present in the SSF file. The file is processed in time order, 
in a tuple-at-a-time fashion to minimize the impact on accuracy. We define 
two classes of rules: \textit{deduplication} and \textit{inference} rules.

### 2013-10-18 paper/kbanotebook2013/content/introduction.tex
small changes in the algorithm
Updated yangs section for him to reviews

We built this system as part of a formal task described in Section~\ref{sec:kbatask}.
In this paper, we describe the system we built to process the data.
Our approach to this task is to build a modular system
that allows us to explore the nuances of the training data and queries.
Overall, our contributions are the following:
\begin{itemize}[noitemsep,nolistsep]
\item we introduce a method to build models of name variations (Section~\ref{section:aliasgeneration});
\item we built a system to filter a large amount of diverse documents (Section~\ref{sec:ccrimpl});
\item we extract entity-slot-value triples of information to be added to KB (Section~\ref{sec:ssve});
\item we filter the final results using deduplication and inference (Section~\ref{section:highAccuracyFilter});
\item we self-evaluate our results over a 4.5 TB data set (Section~\ref{sec:results}).
\end{itemize}

>>>>

In this paper, we describe the system we built to process the data.
We built this system as part of a formal task described in Section~\ref{sec:kbatask}.
Our approach to this task is to build a modular system
that allows us to explore the nuances of the training data and queries.
Overall, we contribute the following:
\begin{itemize}[noitemsep,nolistsep]
\item introduce a method to build models of name variations (Section~\ref{section:aliasgeneration});
\item built a system to filter a large amount of diverse documents (Section~\ref{sec:ccrimpl});
\item extract entity-slot-value triples of information to be added to KB (Section~\ref{sec:ssve});
\item filter the final results using deduplication and inference (Section~\ref{section:highAccuracyFilter});
\item self-evaluate our results over a 4.5 TB data set (Section~\ref{sec:results}).
\end{itemize}
